{\bf Practical Concurrency Testing} \\ \normalsize \vspace{1em} {\em or, How I Learned to Stop Worrying and Love the Exponential Explosion}

### 2016-09-16 proposal/related.tex
write about reduction techniques

{\bf Theoretical advances.}
% TODO

\section{Search Strategies}

% TODO
%etc..

>>>>

{\bf Search Strategies}
To date a number of techniques have been proposed to mitigate exponential explosion, the Sisyphean rock of stateless model checkers.
Dynamic Partial Order Reduction (DPOR) \cite{dpor}, the baseline approach, prunes redundant interleavings by identifying independent thread transitions which can commute without changing the program state.
It is a {\em sound} reduction algorithm, meaning it will never fail to test a possible program behavior, despite skipping many execution sequences.
DPOR has since been extended in several ways:
a provably optimal version which guarantees to explore no more than one interleaving from each equivalence class \cite{optimal-dpor},
% TODO: a 3rd example?
and an extension of the algorithm to include nondeterminism arising from weak memory models \cite{tsopso}.
Recently, SATCheck and Maximal Causality Reduction have emerged as better-performing alternatives to DPOR.
These algorithms use SMT solvers \cite{z3} to identify additional equivalences by analyzing the values read and written by each memory access.

A number of other techniques address the problem that even with DPOR, a state space may be too large.
Iterative Context Bounding (ICB) \cite{chess-icb} is a search ordering heuristic which prioritizes interleavings with fewer preemptions,
according to the insight that most bugs require fewer preemptions to expose.
Bounded Partial Order Reduction \cite{bpor} adapts DPOR to be soundly compatible with ICB.
Preemption Sealing \cite{sealing} allows programmers to exclude preemption points arising from trusted source code modules,
reducing the state space by limiting the scope of the test.
Probabilistic Concurrency Testing \cite{randomized-scheduler} eschews DPOR's depth-first approach entirely (as well as any potential for completing the state space), randomly sampling a broad cross-section of the state space and providing probabilistic bounds on uncovering bugs.

{\bf Other theoretical advances.}
% TODO
